---
title: "day 4 interactive"
format: html
editor: visual
---

```{r}
library(dplyr)
```

## Functions

Make a function that doubles a value.

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}
```

```{r}
double_value(10.13)

double_value(my_dollars = 10.13, 5)
```

```{r}
monthly_income <- c(42.50, 61.75, 89.50)

double_value(monthly_income)
```

Create a function that returns an awesome restaurant name.

```{r}
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}

name_restaurant(animal = "hawk", food = "pizza")
```

Given temperature in degrees Fahrenheit, write a function that converts it to Celsius.

```{r}
fahrenheit_to_celsius <- function(fahrenheit) {
  print((fahrenheit-32) * (5/9))
}

fahrenheit_to_celsius(140)
```

Create a function that given inputs of age and hometown, returns "I am \_\_\_ years old, and I'm from \_\_\_"

```{r}
age_hometown_statement <- function(age, hometown) {
  print(paste("I am", age, "years old, and I'm from", hometown))
}

age_hometown_statement(age = 23, hometown = "Valencia")
```

Print statements and return statements,

Print: "show me", Return: "store this so I can use it later"

## Functions with conditionals

```{r}
calculate_animal_age <- function(species, age_human_years) {
  if (species == "dog") {
    print(age_human_years * 7)
  } else if (species == "goat") {
    print(age_human_years * 4.7)
  } else {
    print("Please enter dog or goat.")
  }
}
```

```{r}
calculate_animal_age(species = "dog", age_human_years = 10)
```

Write a function that, given temperature in Kelvin, if a user selects "metric" for the scale, then return degrees Celsius, or if they select "english" then return degrees in Fahrenheit.

```{r}
convert_kelvin <- function(kelvin, scale) {
  if (scale == "metric") {
    kelvin - 273.15
  } else if (scale == "english") {
    (kelvin - 273.15) * (9/5) + 32
  }
}

convert_kelvin(kelvin = 353, scale = "metric")
```

## More functions

Creating a subset within a function, and then return something based on that subset.

```{r}
dog_choice <- data.frame(dog_name = c("Khora", "Teddy","Waffle", "Bacon", "Tito"),
                         food = c("everything", "salmon", "pancakes", "chicken", "enchiladas" ))
```

```{r}
dog_menu <- function(enter_dog_name) {
  my_subset <- filter(dog_choice, dog_name == enter_dog_name)
  print(paste("My name is", my_subset$dog_name, "and my favorite food is", my_subset$food))
}

dog_menu(enter_dog_name = "Waffle")
```

## Function with a for loop

```{r}
df_means <- function(df) {
  for (i in seq_along(df)) {
    col_mean <- mean(df[[i]], na.rm = TRUE)
    column_name <- colnames(df[i])
    print(paste("The mean value of", column_name, "is", col_mean))
  }
}

df_means(mtcars)

df_means(faithful)
```
