---
title: "day 4 interactive"
format: html
editor: visual
---

## Functions

Make a function that doubles a value.

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}
```

```{r}
double_value(10.13)

double_value(my_dollars = 10.13, 5)
```

```{r}
monthly_income <- c(42.50, 61.75, 89.50)

double_value(monthly_income)
```

Create a function that returns an awesome restaurant name.

```{r}
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}

name_restaurant(animal = "hawk", food = "pizza")
```

Given temperature in degrees Fahrenheit, write a function that converts it to Celsius.

```{r}
fahrenheit_to_celsius <- function(fahrenheit) {
  print((fahrenheit-32) * (5/9))
}

fahrenheit_to_celsius(140)
```

Create a function that given inputs of age and hometown, returns "I am \_\_\_ years old, and I'm from \_\_\_"

```{r}
age_hometown_statement <- function(age, hometown) {
  print(paste("I am", age, "years old, and I'm from", hometown))
}

age_hometown_statement(age = 23, hometown = "Valencia")
```

Print statements and return statements,

Print: "show me", Return: "store this so I can use it later"
